Writing Trash Bin

### 2023-12-18 index.qmd
updated notes and sections after mendeley paper sort

## 2.2 Taxonomies of Uncertainty
More commonly uncertainty is defined using a taxonomy rather than a strict definition.

@@

# 3. Visualisation as a form of uncertainty comunication
## 3.1 General attitudes towards uncertainty
## 3.2 Attitudes towards uncertainty visualisation

# 4. Uncertainty Visualisation Best Practices

>>>>

## 2.2 Taxonomies
### 2.2.1 Taxonomies of Uncertainty
More commonly uncertainty is defined using a taxonomy rather than a strict definition.

@@

### 2.2.1 Taxonomies of Visual Uncertainty

# 3.General Attitudes...
## 3.1 Towards uncertainty in general
## 3.2 Towards uncertainty visualisation

# 4 Uncertainty Visualisation Best Practices
# 4.1 The current landscape of uncertainty visualisation research
# 4.2 Take aways from the literature

### 2023-12-18 writingdumpster.qmd
updated notes and sections after mendeley paper sort

# General Thoughts For Actual Review
##### Introduction
##### Defining Uncertainty
  - The more taxonomies I read the more convinced I am the "defining uncertainty" is the best one. Not only is it the most complete, but it also identifies WHY some uncertainties are difficult to visualise (specifically which part of the taxonomy) and suggests HOW you can best communicate these uncertainties.
    - A lot of other papers just make a comment like "oh some of these are hard to communicate" but that paper actually goes into detail instead of hand waving the problem away.
    - It also explains why the uncertainty visualisation literature focuses on a specific subset of uncertainty cases.
  - Examples
    - Null Values
    - Variance
    - Hypothesis Testing
    - Distribution
  - Combining uncertainty is also a reccurring theme in these papers
- I think it is also important to highlight if uncertainty is meta information or if it is a variable in of itself. Meta information (such as contiunity, exhangeability, etc) are usually set to specific visual features (e.g. VSUP clearly sees uncertainty as meta information)
- A lot of work that evaluates uncertainty visualisations checks to see if the mean can be gathered from a visualisation, but if we view uncertainty as meta-information, then with a high uncertainty we wouldn't want the mean to be visible
  - Also an example of why the motivation matters for these things. If you don't know "WHY" someone is using a visualisation for uncertainty and just pick the "best" one, you are going to get a visualisation that does a poor job of its task.
  - put uncertainty in the context of other meta-data of variables

##### Visualisation as a form of Uncertainty communication
  - Basically I want a brief section highlighting the importance of visualisation and discussing it in relation to other forms of uncertainty communication.
  - especially considering some uncertainty visualisation papers discuss using just a text based method to communicate uncerainty

>>>>

# General Thoughts For Actual Review
##### General
- I might need to go back through and add in notes about general visualisation stuff and bad papers for motivations
- could also help to include a bunch of papers that talk about density visualisation without mentioning uncertainty visualisation in the "context" section. (for now have left those unsorted)

##### Introduction

##### Defining Uncertainty
  - The more taxonomies I read the more convinced I am the "defining uncertainty" is the best one. Not only is it the most complete, but it also identifies WHY some uncertainties are difficult to visualise (specifically which part of the taxonomy) and suggests HOW you can best communicate these uncertainties.
    - A lot of other papers just make a comment like "oh some of these are hard to communicate" but that paper actually goes into detail instead of hand waving the problem away.
    - It also explains why the uncertainty visualisation literature focuses on a specific subset of uncertainty cases.
  - Examples
    - Null Values
    - Variance
    - Hypothesis Testing
    - Distribution
  - Combining uncertainty is also a reccurring theme in these papers
- I think it is also important to highlight if uncertainty is meta information or if it is a variable in of itself. Meta information (such as contiunity, exhangeability, etc) are usually set to specific visual features (e.g. VSUP clearly sees uncertainty as meta information)
- A lot of work that evaluates uncertainty visualisations checks to see if the mean can be gathered from a visualisation, but if we view uncertainty as meta-information, then with a high uncertainty we wouldn't want the mean to be visible
  - Also an example of why the motivation matters for these things. If you don't know "WHY" someone is using a visualisation for uncertainty and just pick the "best" one, you are going to get a visualisation that does a poor job of its task.
  - put uncertainty in the context of other meta-data of variables

##### Visualisation as a form of Uncertainty communication
- A LOT OF the work in uncertainty communication has a sub-field that is visualisation specific
  - Basically I want a brief section highlighting the importance of visualisation and discussing it in relation to other forms of uncertainty communication.
  - especially considering some uncertainty visualisation papers discuss using just a text based method to communicate uncerainty
